AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-17 publications/iaai21/dora_outlier_detection_iaai.tex
Resolve dataset summary table todo. #42

We constructed three datasets to evaluate the utility of DORA and the
performance of each ranking algorithm for a variety of scientific domains
 (astrophysics, planetary science, and Earth science). We also included a 
 benchmark dataset that uses MNIST and Fashion-MNIST. Here we describe
 the details of each dataset.
\todo{Maybe add
 a table with number of samples, number of reference known outliers (if 
 available), etc, if room? }
 \todo{Can we make any of these datasets publicly available with the paper?}

@@

\section{Conclusions}
\todo{
Summarize conclusions and plans for future work
[Note that these datasets could also be used by other researchers as OOD
 benchmark tasks?]
}

>>>>

We constructed three datasets to evaluate the utility of DORA and the
performance of each ranking algorithm for a variety of scientific domains
 (astrophysics, planetary science, and Earth science). We also included a 
 benchmark dataset that uses MNIST and Fashion-MNIST. Table \ref{tab:datasets}
 summarizes the number of unlabeled samples used for training and labeled
 samples used for evaluation for each dataset. We describe each in detail
 below.

@@

\section{Conclusions}
\todo{
Summarize conclusions and plans for future work
[Note that these datasets could also be used by other researchers as OOD
 benchmark tasks?]
 \todo{Can we make any of these datasets publicly available with the paper?}
}
